### 2016-08-11 Chapters/Ch04-PaperSummary.tex
Write summary of third paper

\section*{Paper I. Continuum solvation in the relativistic regime}

@@

\begin{figure}[!htb]
\centering
\scalebox{0.8}{\input{gfx/algorithm.tikz}}
\caption[Modular approach to programming a \acs{PCM} functionality into an existing \acs{SCF} code.]{
  Schematic view of the implemented SCF algorithm. Computations/data in
  \textcolor{Blue}{blue} are on the \pcmsolver side, in
  \textcolor{Green}{green} on the \DIRAC side.
  }
\label{fig:algorithm}
\end{figure}

@@

\section*{Paper II. The wavelet Galerkin boundary element method for PCM}

@@

This work builds upon and extends previous work by~\citeauthor{Weijo2010-hy}
\citeauthor{Weijo2010-hy} used \ac{PWC} bases to show that superior accuracy
and convergence could be obtained for the calculation of molecular energies.
In this work we showed that faster convergence can be achieved when \ac{PWL} bases are used instead.
Moreover, the same holds for the calculation of static electric properties.
Notably, the traditional collocation solver cannot guarantee the same accuracy,
even for very large finite element bases. This suggests that, in some cases,
\acs{BEM} collocation methodologies might slow down or even prevent the
convergence of the quantum mechanical response equations solvers.

@@

\section*{Paper III: Continuum modelling of non homogeneous environments}

@@

In this work, a similar procedure was introduced to tackle diffuse interfaces
in spherical symmetry.
In contrast to previously existing work, our implementation offer a more robust
treatment of thin interfaces, with a rather generic functional form for the
permittivity profile.
We thoroughly analyzed the necessity for the \emph{a posteriori} removal of the
Coulomb singularity from the computed Green's function and its efficient
implementation.
Transfer of ions and molecules across spherically symmetric interfaces exhibits
peculiar properties. These arise as consequence of both interface width and
interface curvature.
In this work, we analyzed both effect on the water-vapor and oil-water transfer
of \ce{Li+}, \ce{Br-}, acetone, \emph{para}-nitroaniline and the L0 dye.

\begin{figure}[tb]
  \centering
  \begin{subfigure}[t]{.49\linewidth}
  \centering
  %\includegraphics[width=.49\linewidth]{placeholder}
  % Figure8a <--> dipole_acetone_perpendicular
\missingfigure{Reobtain this figure}
  \caption{Width effect}
  \label{fig:profile_dipole_acetone_width}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{.49\linewidth}
  \centering
  %\includegraphics[width=.49\linewidth]{placeholder}
  % Figure8b <--> curv_fullprofile_dip_acetone
\missingfigure{Reobtain this figure}
  \caption{Radius effect}
  \label{fig:profile_dipole_acetone_fullprofile}
  \end{subfigure}

  \begin{subfigure}[t]{.49\linewidth}
  \centering
  %\includegraphics[width=.49\linewidth]{placeholder}
  % Figure8c <--> curv_dip_acetone
\missingfigure{Reobtain this figure}
  \caption{Curvature effect}
  \label{fig:profile_dipole_acetone_curvature}
  \end{subfigure}
  \caption[Width, radius and curvature effect on the dipole moment of acetone for water-air droplet phase transfer.]
  {Dipole moment profiles for acetone (with dipole moment
  perpendicular to the interface) transfer at water droplet in air, for
  varying interface widths, values of $R_0$ and the curvature effect on
  dipole moment, respectively.}
  \label{fig:profile_dipole_acetone}
\end{figure}

>>>>

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{Continuum solvation in the relativistic regime}}
\section*{Paper I. Continuum solvation in the relativistic regime}

@@

\begin{figure}[!htb]
\centering
\scalebox{0.8}{\input{gfx/relapcm/algorithm.tikz}}
\caption[Modular approach to programming a \acs{PCM} functionality into an existing \acs{SCF} code.]{
  Schematic view of the implemented SCF algorithm. Computations/data in
  \textcolor{Blue}{blue} are on the \pcmsolver side, in
  \textcolor{Green}{green} on the \DIRAC side.
  }
\label{fig:algorithm}
\end{figure}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{The wavelet Galerkin boundary element method for PCM}}
\section*{Paper II. The wavelet Galerkin boundary element method for PCM}

@@

Already~\citeauthor{Weijo2010-hy} had shown that using \ac{PWC} bases can lead
to superior accuracy and convergence in the calculation of quantum mechanical
molecular solvation energies.
In this work we showed that even faster convergence can be achieved when
\ac{PWL} bases are used instead.
Moreover, the same holds for the calculation of static electric properties.
Notably, the traditional collocation solver cannot guarantee the same accuracy,
even for very large finite element bases. This suggests that, in some cases,
\acs{BEM} collocation methodologies might slow down or even prevent the
convergence of the quantum mechanical response equations solvers.

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{Continuum modelling of non homogeneous environments}}
\section*{Paper III: Continuum modelling of non homogeneous environments}

@@

In this work, a similar procedure was introduced to tackle diffuse interfaces
in spherical symmetry.
In contrast to previously existing work, our implementation offer a more robust
treatment of thin interfaces, with a rather generic functional form for the
permittivity profile.
We thoroughly analyzed the necessity for the \emph{a posteriori} removal of the
Coulomb singularity from the computed Green's function and its efficient
implementation.
Interface width and curvature influence the transfer of ions and molecules across
spherically symmetric interfaces and peculiar properties may arise.
In this work, we analyzed both effect on the water-vapor and oil-water transfer
of \ce{Li+}, \ce{Br-}, acetone, \emph{para}-nitroaniline and the L0 dye.
Nonelectrostatic interactions were not included in our implementation, although
they have been proved to be crucial for non homogeneous
environments.~\autocite{Mozgawa2014-ad}
Nevertheless our implementation represents a first significant step in the continuum treatment
of such nontrivial environments.

\begin{figure}[tb]
  \centering
  \begin{subfigure}[t]{.49\linewidth}
  \centering
  % Figure8a <--> dipole_acetone_perpendicular
  \includegraphics[width=\textwidth]{gfx/spherical/width.png}
  \caption{Width effect}
  \label{fig:profile_dipole_acetone_width}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{.49\linewidth}
  \centering
  % Figure8b <--> curv_fullprofile_dip_acetone
  \includegraphics[width=\textwidth]{gfx/spherical/radius.png}
  \caption{Radius effect}
  \label{fig:profile_dipole_acetone_fullprofile}
  \end{subfigure}

  \begin{subfigure}[t]{.49\linewidth}
  \centering
  % Figure8c <--> curv_dip_acetone
  \includegraphics[width=\textwidth]{gfx/spherical/curvature.png}
  \caption{Curvature effect}
  \label{fig:profile_dipole_acetone_curvature}
  \end{subfigure}
  \caption[Width, radius and curvature effect on the dipole moment of acetone for water-air droplet phase transfer.]
  {Dipole moment profiles for acetone (with dipole moment
  perpendicular to the interface) transfer at water droplet in air, for
  varying interface widths, values of $R_0$ and the curvature effect on
  dipole moment, respectively.}
  \label{fig:profile_dipole_acetone}
\end{figure}

I contributed most of the theoretical work for this paper, based on early drafts from coauthors
Ville Weijo and Hui Cao. In particular, I derived the separation of
the Coulomb singularity in its final form.
Moreover, I contributed the implementation and testing of the Green's function code.
The interface to the \LSDALTON program package, developed within paper II, was
also used for this paper.
I wrote the first draft of the paper and coordinated all subsequent editing stages.

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{Relativistic calculation of EPR and pNMR parameters in solution}}
\section*{Paper IV: Relativistic calculation of EPR and pNMR parameters in solution}

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{Open-ended self-consistent field response theory in solution}}
\section*{Paper V: Open-ended self-consistent field response theory in solution}

### 2016-08-11 FrontBackmatter/Publications.tex
Write summary of third paper

%*******************************************************
% Publications
%*******************************************************
\thispagestyle{empty}
\refstepcounter{dummy}
\pdfbookmark[1]{Publications}{Publications}
\chapter*{Publications}%\graffito{This is just an early --~and currently ugly~-- test!}

@@

\end{enumerate}

>>>>

%*******************************************************
% Publications
%*******************************************************
\thispagestyle{empty}
\refstepcounter{dummy}
\pdfbookmark[1]{Publications}{Publications}
\chapter*{Publications}

@@

\item
  \textbf{R. Di Remigio}, M. Repisky, S. Komorovsky, P. Hrobarik, L.
  Frediani, and K. Ruud
  \\
  Four-Component Relativistic Density Functional Theory with the
  Polarizable Continuum Model: Application to EPR Parameters
  and Paramagnetic NMR Shifts
  \\
  submitted for publication to \textit{Mol. Phys.}
\label{pcmepr}

\item
  \textbf{R. Di Remigio}, M. T. P. Beerepoot, Y. Cornaton, M. Ringholm,
  A. H. S. Steindal, K. Ruud, and L. Frediani
  \\
  Open-ended formulation of self-consistent field response theory with
  the polarizable continuum model for solvation
  \\
  In preparation for submission to \textit{Phys. Chem. Chem. Phys.}
\label{pcmopenrsp}
\end{enumerate}

The following proceeding is also part of the thesis:
\begin{enumerate}
\item
  \textbf{R. Di Remigio}, T. D. Crawford, and L. Frediani
  \\
  PCMSolver: an Application Programming Interface
  for the Polarizable Continuum Model
  \\
  Accepted for publication in the proceedings of the
  \emph{Producing High Performance and Sustainable Software for
  Molecular Simulation} workshop held at the 2015 Supercomputing
  Conference
\label{SC15}
\end{enumerate}
